---
title: "A Guide to AbunRNA"
author: "ChengYue Zhang"
date: "`r format(Sys.time(), '%d %b %Y')`"
output: 
  rmarkdown::html_vignette:
    toc: true
    number_sections: false
vignette: >
  %\VignetteIndexEntry{A Guide to AbunRNA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(fig.align = "center", 
               out.width = "90%",
               fig.width = 6, fig.height = 5.5,
               dev.args=list(pointsize=10),
               par = TRUE, # needed for setting hook 
               collapse = TRUE, # collapse input & ouput code in chunks
               warning = FALSE)
knit_hooks$set(par = function(before, options, envir)
  { if(before && options$fig.show != "none") 
       par(family = "sans", mar=c(4.1,4.1,1.1,1.1), mgp=c(3,1,0), tcl=-0.5)
})
set.seed(1) # for exact reproducibility
```
       
## Introduction

`AbunRNA` is an R package developed to wrap up the commonly used RNA-seq analysis pipelines from the initial quality check, sanity check, to quantification on transcript expression, then to the downstream analysis.

To download **AbunRNA**, use the following commands:

``` r
require("devtools")
install_github("zhangchengyue/AbunRNA", build_vignettes = TRUE)
library("AbunRNA")
```
To list all sample functions available in the package:
``` r
ls("package:AbunRNA")
```

To list all sample datasets available in the package:
``` r
data(package = "AbunRNA")
```

<br>


<br>

## Minimal requirements
* The **R subdirectory**
* The **man subdirectory**
* **DESCRIPTION** file
* **NAMESPACE** file

### Other
* **README** file
* **LICENSE** file
* The **data** subdirectory
* The **tests** subdirectory
* The **vignettes** subdirectory
* The **inst** subdirectory

<br>
<div style="text-align:left">

## Package References

[Zhang, CY. (2022) AbunRNA: R Package For
  RNA abundance analysis. Unpublished.](https://github.com/zhangchengyue/AbunRNA)

<br>

## Other References





----

```{r}
sessionInfo()
```
